Staged Abstract Interpreters

### 2019-03-25 paper/20_prelim.tex
tweak code

\paragraph{Concrete Components}
Now we can instantiate the interpreter as a standard environment-store
interpreter. Such interpreter can be obtained by refunctionalization of CESK
machines \cite{Felleisen:1987:CAH:41625.41654, DBLP:conf/ppdp/AgerBDM03}.
The two types we need to concretize are @Addr@ and @Value@, afterward, the @Env@
and @Store@ is concretized automatically. To assure the freshness, we use @Int@
for the address space @Addr@. A value can be either a tagged number
\texttt{IntV}, or a closure \texttt{CloV} that contains a lambda term and an
environment. The final return value of the interpreter is a pair of values and
stores, where the @Value@ and @Store@ are obviously next-stage objects. We also
provide a standard fixed-point combinator to close the open-recursive function @ev@.

>>>>

Now we can instantiate the interpreter as a standard environment-store
interpreter. Such interpreter can be obtained by refunctionalization of CESK
machines \cite{Felleisen:1987:CAH:41625.41654, DBLP:conf/ppdp/AgerBDM03}.

\paragraph{Concrete Components}
The two types we need to concretize are @Addr@ and @Value@, afterward, the @Env@
and @Store@ is concretized automatically. To assure the freshness, we use @Int@
for the address space @Addr@. A value can be either a tagged number
\texttt{IntV}, or a closure \texttt{CloV} that contains a lambda term and an
environment. The final return value of the interpreter is a pair of values and
stores, where the @Value@ and @Store@ are obviously next-stage objects. We also
provide a standard fixed-point combinator to close the open-recursive function @ev@.

### 2019-03-25 paper/60_cases.tex
tweak code

\begin{figure*}
  \centering
  \begin{subfigure}[h]{0.49\textwidth}
    \centering
    \begin{lstlisting}
type CompAnalysis = Store => Store
def compProgram(prog: Expr): CompAnalysis = compCall(prog)
def compCall(call: Expr): CompAnalysis = call match {
  case Letrec(bds, body) =>
    val C1 = compCall(body); val C2 = compArgs(bds.map(_.value))
    ($\sigma$: Store) => C1(C2($\sigma$.update(bds.map(_.name), 
       bds.map(b => Set(b.value.asInstanceOf[Lam])))))
  case App(f, args) =>
    val C1 = compApp(f, args); val C2 = compArgs(args)
    ($\sigma$: Store) => C1(C2($\sigma$))
}
def compApp(f: Expr, args: List[Expr]): CompAnalysis = 
  f match {
    case Var(x) => ($\sigma$: Store) => 
      analysisAbsApp($\sigma$.lookup(x), args, $\sigma$)
    case Op(_) => compArgs(args)
    case Lam(vars, body) =>
      val C = compCall(body)
      ($\sigma$: Store) => 
        C($\sigma$.update(vars, args.map(primEval(_, $\sigma$))))
  }
def compArgs(args: List[Expr]): CompAnalysis = args match {
  case Nil => ($\sigma$: Store) => $\sigma$
  case (arg@Lam(vars, body))::rest =>
    val C1 = compCall(body); val C2 = compArgs(rest)
    ($\sigma$: Store) => C2(C1($\sigma$))
  case _::rest => compArgs(rest)
}
  \end{lstlisting}
  \end{subfigure}
\hfill
  \begin{subfigure}[h]{0.49\textwidth}
    \centering
    \begin{lstlisting}
def analyzeProgram(prog: Expr, $\sigma$: Rep[Store]): Rep[Store] = 
  analyzeCall(prog, $\sigma$)
def analyzeCall(call: Expr, $\sigma$: Rep[Store]): Rep[Store] = 
  call match {
    case App(f, args) => analyzeApp(f, args, analyzeArgs(args, $\sigma$))
    case Letrec(bds, body) =>
      val $\sigma$_* = $\sigma$.update(bds.map(_.name), 
        bds.map(b => Set(b.value.asInstanceOf[Lam])))
      val $\sigma$_** = analyzeArgs(bds.map(_.value), $\sigma$_*)
      analyzeCall(body, $\sigma$_**)
  }
def analyzeApp(f: Expr, args: List[Expr], $\sigma$: Rep[Store]): 
  Rep[Store] = f match {
    case Var(x) => analyzeAbsApp(args, $\sigma$(x), $\sigma$)
    case Op(_) => analyzeArgs(args, $\sigma$)
    case Lam(vars, body) =>
      val $\sigma$_* = $\sigma$.update(vars, args.map(primEval(_, $\sigma$)))
      analyzeCall(body, $\sigma$_*)
  }
def analyzeArgs(args: List[Expr], $\sigma$: Rep[Store]): Rep[Store] = 
  args match {
    case Nil => $\sigma$
    case Lam(vars, body)::rest => 
      analyzeArgs(rest, analyzeCall(body, $\sigma$))
    case _::rest => analyzeArgs(rest, $\sigma$)
  }
  \end{lstlisting}

>>>>

\begin{figure*}
  \centering
  \begin{subfigure}[h]{0.49\textwidth}
    \centering
    \begin{lstlisting}[
      language=Scala,%
      mathescape=true,%
      %  columns=[c]fixed,%
      %  basewidth={0.5em, 0.40em},%
      aboveskip=2pt,%\smallskipamount,
      belowskip=1pt,%\negsmallskipamount,
      lineskip=-1pt,
      basewidth={0.6em, 0.45em},%
      %  backgroundcolor=\color{listingbg},
      basicstyle=\fontsize{6}{8}\selectfont\ttfamily,
      keywordstyle=\keywordstyle,
      commentstyle=\commentstyle,
      stringstyle=\stringstyle,
    ]
type CompAnalysis = Store => Store
def compProgram(prog: Expr): CompAnalysis = compCall(prog)
def compCall(call: Expr): CompAnalysis = call match {
  case Letrec(bds, body) =>
    val C1 = compCall(body); val C2 = compArgs(bds.map(_.value))
    ($\sigma$: Store) => C1(C2($\sigma$.update(bds.map(_.name), 
       bds.map(b => Set(b.value.asInstanceOf[Lam])))))
  case App(f, args) =>
    val C1 = compApp(f, args); val C2 = compArgs(args)
    ($\sigma$: Store) => C1(C2($\sigma$))
}
def compApp(f: Expr, args: List[Expr]): CompAnalysis = 
  f match {
    case Var(x) => ($\sigma$: Store) => 
      analysisAbsApp($\sigma$.lookup(x), args, $\sigma$)
    case Op(_) => compArgs(args)
    case Lam(vars, body) =>
      val C = compCall(body)
      ($\sigma$: Store) => C($\sigma$.update(vars, args.map(primEval(_, $\sigma$))))
  }
def compArgs(args: List[Expr]): CompAnalysis = args match {
  case Nil => ($\sigma$: Store) => $\sigma$
  case (arg@Lam(vars, body))::rest =>
    val C1 = compCall(body); val C2 = compArgs(rest)
    ($\sigma$: Store) => C2(C1($\sigma$))
  case _::rest => compArgs(rest)
}
  \end{lstlisting}
  \end{subfigure}
\hfill
  \begin{subfigure}[h]{0.49\textwidth}
    \centering
    \begin{lstlisting}[
      language=Scala,%
      mathescape=true,%
      %  columns=[c]fixed,%
      %  basewidth={0.5em, 0.40em},%
      aboveskip=2pt,%\smallskipamount,
      belowskip=1pt,%\negsmallskipamount,
      lineskip=-1pt,
      basewidth={0.6em, 0.45em},%
      %  backgroundcolor=\color{listingbg},
      basicstyle=\fontsize{6}{8}\selectfont\ttfamily,
      keywordstyle=\keywordstyle,
      commentstyle=\commentstyle,
      stringstyle=\stringstyle,
    ]
def analyzeProgram(prog: Expr, $\sigma$: Rep[Store]): Rep[Store] = 
  analyzeCall(prog, $\sigma$)
def analyzeCall(call: Expr, $\sigma$: Rep[Store]): Rep[Store] = 
  call match {
    case App(f, args) => analyzeApp(f, args, analyzeArgs(args, $\sigma$))
    case Letrec(bds, body) =>
      val $\sigma$_* = $\sigma$.update(bds.map(_.name), 
        bds.map(b => Set(b.value.asInstanceOf[Lam])))
      val $\sigma$_** = analyzeArgs(bds.map(_.value), $\sigma$_*)
      analyzeCall(body, $\sigma$_**)
  }
def analyzeApp(f: Expr, args: List[Expr], $\sigma$: Rep[Store]): 
  Rep[Store] = f match {
    case Var(x) => analyzeAbsApp(args, $\sigma$(x), $\sigma$)
    case Op(_) => analyzeArgs(args, $\sigma$)
    case Lam(vars, body) =>
      val $\sigma$_* = $\sigma$.update(vars, args.map(primEval(_, $\sigma$)))
      analyzeCall(body, $\sigma$_*)
  }
def analyzeArgs(args: List[Expr], $\sigma$: Rep[Store]): Rep[Store] = 
  args match {
    case Nil => $\sigma$
    case Lam(vars, body)::rest => 
      analyzeArgs(rest, analyzeCall(body, $\sigma$))
    case _::rest => analyzeArgs(rest, $\sigma$)
  }
  \end{lstlisting}
